\thesistitle

### 2019-07-25 sections/clonerefactor.tex
Removing redundant clone classes

\subsubsection{Removing redundant clone classes}\label{sec:conceptualremovingredundant}
\ana{MOVE THIS, Part of the clone class collection and one that is found but not yet part of the collection. If the new one is a subset of the one in the collection then it is ignored. If the new one is a superset of any clone in the collection it replaces those. If one is a subset of the other it should be replaced.}

The clone detection method used by CloneRefactor can, for various reasons,%Should I list these? Listing them could be a section on its own, as I'd have to show examples to make it concrete.
result in redundant clone classes. After the insertion of each newly detected clone, we check whether it is redundant and/or any of the existent clones has become redundant by adding this clone. A clone is redundant if it is a subset of another clone. We define the subset relation between clones as follows:

\begin{equation}\label{eq:subset}
C_1 \subseteq C_2 \Leftrightarrow \forall (i_1 \in C_1) \text{ } \exists (i_2 \in C_2) \text{ } F i_1 = F i_2 \wedge R i_1 \subseteq R i_2
\end{equation} % Right symbol for definition

>>>>

\subsubsection{Removing redundant clone classes}\label{sec:conceptualremovingredundant}
The clone detection method used by CloneRefactor can, for various reasons,%Should I list these? Listing them could be a section on its own, as I'd have to show examples to make it concrete.
result in redundant clone classes. After the insertion of each newly detected clone, we check whether it is redundant and/or any of the existent clones has become redundant by adding this clone. A clone is redundant if it is a subset of another clone. We define the subset relation between clones as follows:

\begin{equation}\label{eq:subset}
C_1 \subseteq C_2 := \forall (i_1 \in C_1) \text{ } \exists (i_2 \in C_2) \text{ } F i_1 = F i_2 \wedge R i_1 \subseteq R i_2
\end{equation} % Right symbol for definition
